RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-21 paper/paper7/paper7.tex
feedback

In this paper, we propose a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
We show how data in rectangular format and metadata on person-level data sets (i.e., data about individuals, households, businesses), aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.
We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality and trust.
We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.

\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
\end{abstract}

@@

For data archives, research institutes, and data libraries,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world as DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}}.
Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints. 
There are also constraint languages like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} that more or less explicitly address the \emph{SBE} community.
In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and RDF data validation.
In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.

Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
which is available for contribution at \url{http://purl.org/net/rdf-validation}.
The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
Bosch and Eckert \cite{BoschEckert2014-2} use SPIN as basis to define a
validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL. 
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.

@@

By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Researchers typically represent their results as aggregated data in form of two-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e. multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}. 
Aggregated data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
%The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
%Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
%allowing the RDF versions of these standards to retain that alignment.
While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
both on a different level of aggregation, 
the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
%Although, in most cases aggregated data is still published in form of PDFs, 
%it is more and more common to publish aggregated data as CSV files,
Aggregated data is more and more published as CSV files,
allowing to perform first data calculations.
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent data in a rectangular format. 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length.

For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
as person-level data include additional variables needed for further research.
%Although not that common, the other direction is also possible, 
%i.e. researchers may use metadata on person-level data to search for aggregated data.
One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
A \emph{study} represents the process by which a data set was generated or collected.
Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} is the statistical office of the European Union. Its task is to provide statistics at European level that enable comparisons between countries and regions.
Eurostat provides publicly available European aggregated data (downloadable as CSV files) and its metadata.
This way, researchers get promising findings (in form of published tables with a few columns), e.g., about the availability of childcare services in European Union Member States by year, duration, and child age  leading to subsequent research questions.
%The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.

The variable \emph{formal childcare}\footnote{The data set is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} (in contrast to childcare at home)
captures the measured availability of childcare services in percent over the population.
The present data collection refers to data on formal childcare by the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20'). 
To determine if variables measuring \emph{age} 
- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable, both content-driven and technology-driven constraints are validated.
Content-driven constraints ensure that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models and 
technology-driven constraints can be generated completely automatically out of vocabularies' data models. 
Examples for content-driven constraints are to investigate (1) if variables are represented in a compatible way,
i.e. are the variables' code lists theoretically comparable, and (2) if variables' code lists are properly structured.
With technology-driven constraints, it can be validated (1) if variable definitions are available and (2) if for each code an associated category (a human-readable label) is specified.

@@

In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.

@@

\section{Related Work}

@@

@@

We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS} (section \ref{implementation}).
We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).

%It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the (meta)data quality of real world \emph{XKOS} and \emph{PHDD} data sets.

>>>>

In this paper, we propose a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary\tb{vocabulary-independent}. 
Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
We show how data in rectangular format and metadata on record-unit data sets (i.e., data about individuals, households, businesses) or more specifically person-level data sets, aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.\tb{record-unit or more specific person-level data sets}
We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality and trust.
We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.
\tb{DCAT und XKOS nur im future work}
\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
\end{abstract}

@@

For data archives, research institutes, and data libraries,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world as DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}} (section \ref{related-work}).
Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints. 
There are also constraint languages like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} that more or less explicitly address the \emph{SBE} community.
In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and RDF data validation.
In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.

Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
which is available for contribution at \url{http://purl.org/net/rdf-validation}.
The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
Bosch and Eckert \cite{BoschEckert2014-2} \tb{why do we use spin?}use SPIN as basis to define a
validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL. 
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.

@@

By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Researchers typically represent their results as aggregated data in form of two-, three-, or four-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e. multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}. 
Aggregated data is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
%The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
%Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
%allowing the RDF versions of these standards to retain that alignment.
While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
both on a different level of aggregation, 
the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
%Although, in most cases aggregated data is still published in form of PDFs, 
%it is more and more common to publish aggregated data as CSV files,
Aggregated data is more and more published as CSV files,
allowing to perform first data calculations.
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent data in a rectangular format. 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length.

For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
as person-level data include additional variables needed for further research.
%Although not that common, the other direction is also possible, 
%i.e. researchers may use metadata on person-level data to search for aggregated data.
One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
A \emph{study} represents the process by which a data set was generated or collected.
Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} is the statistical office of the European Union. Its task is to provide statistics at European level that enable comparisons between countries and regions.
Eurostat provides publicly available European aggregated data (downloadable as CSV files) and its metadata.
This way, researchers get promising findings (in form of published tables with a few columns).

We use the availability of childcare services in European Union Member States by year, duration, and child age leading to subsequent research questions as running example of this paper.\tb{nochmals drüber schauen}
%The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
The variable \emph{formal childcare}\footnote{The data set is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} (in contrast to childcare at home)
captures the measured availability of childcare services in percent over the population.
The present data collection refers to data on formal childcare by the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20').

To determine if variables measuring \emph{age}\tb{vielleicht zu den letzten paragraphen hinzufügen} 
- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable, both content-driven and technology-driven constraints are validated.
Content-driven constraints ensure that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models and 
technology-driven constraints can be generated completely automatically out of vocabularies' data models. 
Examples for content-driven constraints are to investigate (1) if variables are represented in a compatible way,
i.e. are the variables' code lists theoretically comparable, and (2) if variables' code lists are properly structured.
With technology-driven constraints, it can be validated (1) if variable definitions are available and (2) if for each code an associated category (a human-readable label) is specified.

@@

In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
\tb{reihenfolge / DCAT fehlt}

@@

\section{Related Work}
\label{related-work}

@@

%validation or relational databases: types, relations

@@

We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS} (section \ref{implementation}).
We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
\tb{auswahl an constraints, die validiert werden sollen / je nach use cases sollen z.b. nur technology-driven constraints validiert werden oder sind wichtiger / use solen je nach use case selbt bestimmen welche constraints validiert werden sollen}
%It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the (meta)data quality of real world \emph{XKOS} and \emph{PHDD} data sets.
